---
title: "Practice github"
author: "Daniel Paulson"
date: "March 13, 2019"
output: html_document
---
```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Loaded the tidyverse package and the package to read excel files

```{r, warning=FALSE, include=TRUE, message=FALSE}
library(readxl)     
library(tidyverse) 
```

###Make the excel file read to finches

```{r}

finches <- read_excel("finches_data.xlsx")
```

###Make the finches data a tibble

```{r}
finches
```

###Able to look at the finches data set
```{r}
glimpse(finches)
```

###Plot a histogram
```{r}
ggplot(
  data = finches,
  mapping = aes(x = beak_length,
                fill = outcome)
) +
  geom_histogram(bins = 14) +  
   facet_wrap(~ outcome, ncol = 1) +
  guides(fill = FALSE) +  
   labs(
    title = "Figure 1.", 
     x = "Beak Length (mm)", 
   y = "Number of Birds" 
   )
```

###Summarize the data
```{r}
beak_length_grouped_summary <- 
  finches %>% 
  group_by(outcome) %>% 
  summarize(mean = mean(beak_length),
            sd = sd(beak_length),
            n = n()) %>% 
  mutate(sem = sd / sqrt(n),
         upper = mean + 1.96 * sem,
         lower = mean - 1.96 * sem)
```

###Print results in the console
```{r}
beak_length_grouped_summary
```

###Make a bar chart
```{r}
ggplot(
  data = beak_length_grouped_summary,
  mapping = aes(x = outcome, 
                y = mean, 
                 fill = outcome)
) +
  geom_col() + 
  geom_errorbar(
    mapping = aes(ymin = lower,
                   ymax = upper),
    width = .3  
  ) +
  guides(fill = FALSE) +
   labs(
    title = "Figure 2.", 
     x = "Survival Outcome",
     y = "Beak Length (mm)"
   )
```

###Get vector for birds that died
```{r}
beak_length_died <-
  finches %>% 
  filter(outcome == "died") %>%
  pull(beak_length) 
```

###Print object in console
```{r}
beak_length_died
```

###Get vector of beak lenghts for birds that survived
```{r}
beak_length_survived <-
  finches %>% 
  filter(outcome == "survived") %>% 
  pull(beak_length)
```

###Print results in console
```{r}
beak_length_survived
```

###Perform a t-test
```{r}
t.test(beak_length_died, beak_length_survived)
```

